---
title: "Bilan_Bresle"
author: "Mathieu Buoro, Quentin Josset & Etienne Prévost"
date: "4/14/2020"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
wdir <- "/media/HDD12To/mbuoro/ORE-DiaPFC/Abundance/"
#setwd(wdir)

site <- "Bresle"
year <- 2024

#COL <- c("yellowgreen","hotpink2","steelblue1","black")
mycol=c("#787878", "#1E90FF", "#a1dab4", "#FF6A6A")

```

### NOTA BENE  
#2022
- pris en compte des arrets de piegages pour la devalaison des adultes
#2020  
- Smolt: la saison de piégeage en dévalaison a couru du 2/12/2019 au 16/3/2020, avant l'arrêt confinement COVID.  
- Adulte: reprise piegage le 11 mai, pas de PHM n'ont pu être capture  
- Prise en compte de l'arret des pièges pendant les weekends (depuis 2018) dans les modèles  

#2019  
- Smolt: arret piegeage weekend / marquage pit (test de mortalite marquage)  

#2018  
- Smolt: arret piegeage weekend / transition marquage pit   




### TABLEAU BILAN


```{r, echo = FALSE}
years <- seq(1982, year, 1)
table <- array(, dim=c(length(years), 5))
colnames(table) <- c( "Année","Tacon 0+","Smolts (tous)", 	"1HM (échappement)",	"PHM (échappement)")
rownames(table) <- years
smolt.years <- years
table[,1] <- years


# ## PARR (from 1993 to now on)
# stade <- "tacon"
# dir <-  paste(wdir,site,"/",stade,sep="")
# if (file.exists(dir)){
#   load(paste0(stade,"/results/Results_",stade,"_",year,".RData"))
#   n_parr <- fit$median$ntot_Sc
   table[,2] <- NA #round(n_parr,0) # 1995 to now
# }


## SMOLTS (from 1982 to now on)
stade <- "smolt"
dir <-  paste(wdir,site,"/",stade,sep="")
if (file.exists(dir)){
  load(paste0(stade,"/results/Results_",stade,"_",year,".RData"))
  n_smolt <- fit$median$Nesc # escapement from river
#table[2:nrow(table),3] <- round(n_smolt,0) # 1995 to now
}

    table[1:6,3] <- round(n_smolt[1:6],0) # 1982 to 1987
    table[11:19,3] <- round(n_smolt[7:15],0) # 1992 to 2000
    table[21:nrow(table),3] <- round(n_smolt[16:length(n_smolt)],0) # 2002 to now

## ADULTS (1994 to now)
stade <- "adult"
dir <-  paste(wdir,site,"/",stade,sep="")
if (file.exists(dir)){
  load(paste0(stade,"/results/Results_",stade,"_",year,".RData"))
  
  # n returns
  n_1SW <- fit$median$n_1SW # 1SW
  n_MSW <- fit$median$n_MSW #  MSW
  # table[3:nrow(table),4] <- round(n_1SW,0) # 1995 to now
  # table[3:nrow(table),5] <- round(n_MSW,0) # 1995 to now
  j=0
  for (i in 3:length(years)){
    j=j+1
    table[i,4] <- round(n_1SW[j],0) # 1995 to now
  }
  k=0
    for (i in 3:length(years)){
      k=k+1
    table[i,5] <- round(n_MSW[k],0) # 1995 to now
  }
}


#write.csv(round(table,2), file=paste('~/Documents/RESEARCH/PROJECTS/ORE/Abundance/CIEM/Table9_',site,"_",year,'.csv',sep=""))
con <- file(paste0("Bilan_",site,"_",year,'.csv'), open="wt")
write.csv( table, con, row.names = FALSE)
close(con)

library(knitr)
kable(table, row.names = FALSE, caption = paste0("Tableau bilan pour le ",site,". Seules les valeurs médianes sont reportées"))

```

## ADULTES

Blablabla

## Nombre total de retour et échappement

```{r pressure, echo=FALSE}
#### RETURNS
years <- seq(1984, year, 1)
stade <- "adult"
#dir <-  paste(wdir,site,"/",stade,sep="")
#if (file.exists(dir)){
# load dataset
load(paste(stade,"/data/data_",stade,"_",year,'.Rdata',sep="")) # chargement des données
load(paste0(stade,"/results/Results_",stade,"_",year,".RData"))
#}


tmp <- as.matrix(fit$sims.matrix)

#png(paste0(site,"/total_return.png"),width = 780, height = 480)
par(mfrow=c(1,1)) 

### Total number of returns
plot(NULL,xlim=c(1,data$Y),ylim=c(0,500),bty="n",ylab="Nombre total de retour",xaxt="n",xlab="")
axis(side=1,line=1,labels = years,at=1:data$Y, las=2, cex.axis=.7)

# N total
mcmc <- as.matrix(tmp[,paste0("n_tot[",1:data$Y,"]")]) # 1984 to now)
n <- t(apply(mcmc,2,quantile,probs=c(0.025, .5, 0.975)))
segments(1:data$Y,n[,"2.5%"], 1:data$Y,n[,"97.5%"], col=paste0(mycol[3]))
lines(n[,"50%"],lty=1,lwd=2,col=mycol[3],type="o")
points(1:data$Y,n[,"50%"],col=mycol[3],pch=21,bg=paste0(mycol[3]))

# Escapement
# mcmc <- as.matrix(tmp[,paste0("e_tot[",1:data$Y,"]")]) # 1984 to now)
# e <- t(apply(mcmc,2,quantile,probs=c(0.025, .5, 0.975)))
# segments(1:data$Y,e[,"2.5%"], 1:data$Y,e[,"97.5%"], col=paste0(mycol[4]))
# lines(e[,"50%"],lty=1,lwd=2,col=mycol[4],type="o")
# points(1:data$Y,e[,"50%"],col=mycol[4],pch=21,bg=paste0(mycol[4]))

#legend("topright", legend=c("Nombre total de retour"), col=mycol[3],lty=1,lwd=2,bty="n")
```


# Nombre total de retour par classe d'âge

```{r, echo=FALSE}


plot(NULL,xlim=c(1,data$Y),ylim=c(0,500),bty="n",ylab="Nombre total de retour",xaxt="n",xlab="")
axis(side=1,line=1,labels = years,at=1:data$Y, las=2, cex.axis=.7)
mycol=c("#787878", "#1E90FF", "#a1dab4", "#FF6A6A")

# 1SW
mcmc <- as.matrix(tmp[,paste0("n_1SW[",1:data$Y,"]")]) # 1984 to now)
n_1SW <- t(apply(mcmc,2,quantile,probs=c(0.025, .5, 0.975)))
segments(1:data$Y,n_1SW[,"2.5%"], 1:data$Y,n_1SW[,"97.5%"], col=paste0(mycol[1]))
lines(n_1SW[,"50%"],lty=1,lwd=2,col=mycol[1],type="o")
points(1:data$Y,n_1SW[,"50%"],col=mycol[1],pch=21,bg=paste0(mycol[1]))

# MSW
mcmc <- as.matrix(tmp[,paste0("n_MSW[",1:data$Y,"]")]) # 1984 to now)
n_MSW <- t(apply(mcmc,2,quantile,probs=c(0.025, .5, 0.975)))
segments(1:data$Y,n_MSW[,"2.5%"], 1:data$Y,n_MSW[,"97.5%"], col=paste0(mycol[2]))
lines(n_MSW[,"50%"],lty=1,lwd=2,col=mycol[2],type="o")
points(1:data$Y,n_MSW[,"50%"],col=mycol[2],pch=21,bg=paste0(mycol[2]))

legend("topright", legend=c("1HM","PHM"), col=mycol[1:2],lty=1,lwd=2,bty="n")


#dev.off()


```

# Proportion de saumon capturés à Beauchamps

Trap not working in 1989, 1993, 2000 & 2001
```{r, echo=FALSE}

#### CAPTURE AT Beauchamps ####
par(mfrow=c(1,1)) 

p <- c(1:5,7:9,11:15,19:data$Y)
mcmc <- as.matrix(tmp[,paste0("pi_B[",p,",1]")]) # 
piMP_1SW <- t(apply(mcmc,2,quantile,probs=c(0.025, .5, 0.975)))*100
mcmc <- as.matrix(tmp[,paste0("pi_B[",p,",2]")]) # 
piMP_MSW <- t(apply(mcmc,2,quantile,probs=c(0.025, .5, 0.975)))*100
### Total number of returns
#png("report/total_return.png",width = 780, height = 480)
plot(NULL,xlim=c(1,data$Y),ylim=c(0,50),bty="n",ylab="% capturé at Beauchamps",xaxt="n",xlab="")#,main="% MSW to be captured by fishing")
axis(side=1,line=1,labels = years,at=1:data$Y, las=2, cex.axis=.7)
gap=0.1
# N total
segments(p+gap,piMP_MSW[,"2.5%"], p+gap,piMP_MSW[,"97.5%"], col=paste0(mycol[4]))
#lines(piMP_MSW[,"50%"],lty=1,lwd=2,col=mycol[4],type="o")
points(p+gap,piMP_MSW[,"50%"],col=mycol[4],pch=21,bg=paste0(mycol[4]),type='b')

# N total
segments(p-gap,piMP_1SW[,"2.5%"], p-gap,piMP_1SW[,"97.5%"], col=paste0(mycol[3]))
#lines(piMP_1SW[,"50%"],lty=1,lwd=2,col=mycol[3],type="o")
points(p-gap,piMP_1SW[,"50%"],col=mycol[3],pch=21,bg=paste0(mycol[3]),type='b')

legend("topright", legend=c("1HM", "PHM"), col=mycol[3:4],lty=1,lwd=3,bty="n")

```

```{r, echo=FALSE}

#### CAPTURE AT Beauchamps ####
par(mfrow=c(1,1)) 

p <- c(1:data$Y)
mcmc <- as.matrix(tmp[,paste0("pi_Eu[",p,",1]")]) # 
piMP_1SW <- t(apply(mcmc,2,quantile,probs=c(0.025, .5, 0.975)))*100
mcmc <- as.matrix(tmp[,paste0("pi_Eu[",p,",2]")]) # 
piMP_MSW <- t(apply(mcmc,2,quantile,probs=c(0.025, .5, 0.975)))*100
### Total number of returns
#png("report/total_return.png",width = 780, height = 480)
plot(NULL,xlim=c(1,data$Y),ylim=c(0,100),bty="n",ylab="% capturé à EU",xaxt="n",xlab="")#,main="% MSW to be captured by fishing")
axis(side=1,line=1,labels = years,at=1:data$Y, las=2, cex.axis=.7)
gap=0.1
# N total
segments(p+gap,piMP_MSW[,"2.5%"], p+gap,piMP_MSW[,"97.5%"], col=paste0(mycol[4]))
#lines(piMP_MSW[,"50%"],lty=1,lwd=2,col=mycol[4],type="o")
points(p+gap,piMP_MSW[,"50%"],col=mycol[4],pch=21,bg=paste0(mycol[4]),type='b')

# N total
segments(p-gap,piMP_1SW[,"2.5%"], p-gap,piMP_1SW[,"97.5%"], col=paste0(mycol[3]))
#lines(piMP_1SW[,"50%"],lty=1,lwd=2,col=mycol[3],type="o")
points(p-gap,piMP_1SW[,"50%"],col=mycol[3],pch=21,bg=paste0(mycol[3]),type='b')

legend("topright", legend=c("1HM", "PHM"), col=mycol[3:4],lty=1,lwd=3,bty="n")

```



# SMOLTS

## Nombre de smolts estimés
```{r smolt, echo=FALSE}

years<-1982:(year)
stade <- "smolt"
#dir <-  paste(wdir,site,"/",stade,sep="")
#if (file.exists(dir)){
# load dataset
load(paste(stade,"/data/data_",stade,"_",year,'.Rdata',sep="")) # chargement des données
load(paste0(stade,"/results/Results_",stade,"_",year,".RData"))
#}


tmp <- as.matrix(fit$sims.matrix)

#png(paste0(site,"/total_return.png"),width = 780, height = 480)
par(mfrow=c(1,1)) 

### Total number of returns
plot(NULL,xlim=c(1,data$Nyears),ylim=c(0,10000),bty="n",ylab="Nombre total de smolts",xaxt="n",xlab="")
axis(side=1,line=1,labels = years,at=1:data$Nyears, las=2, cex.axis=.7)

# N total
p <- c(1:6,11:19,21:data$Nyears)
mcmc <- as.matrix(tmp[,paste0("Ntot[",p,"]")])    
n <- t(apply(mcmc,2,quantile,probs=c(0.025, .5, 0.975)))
segments(p,n[,"2.5%"], p,n[,"97.5%"], col=paste0(mycol[1]))
#lines(n[,"50%"],lty=1,lwd=2,col=mycol[1],type="o")
points(p,n[,"50%"],col=mycol[1],pch=21,bg=paste0(mycol[1]))

# Escapment
# mcmc <- as.matrix(tmp[,paste0("Nesc[",p,"]")])    
# n <- t(apply(mcmc,2,quantile,probs=c(0.025, .5, 0.975)))
# segments(p,n[,"2.5%"], p,n[,"97.5%"], col=paste0(mycol[2]))
# #lines(n[,"50%"],lty=1,lwd=2,col=mycol[2],type="o")
# points(p,n[,"50%"],col=mycol[2],pch=21,bg=paste0(mycol[2]))

#legend("topright", legend=c("Nombre total de smolts", "Echappement"), col=mycol[1:2],lty=1,lwd=2,bty="n")

```

 TO DO: % smolts captured at traps
```{r capt_smolt, echo=FALSE}
# par(mfrow=c(1,1)) 
# 
# ### Total number of returns
# plot(NULL,xlim=c(1,data$Nyears),ylim=c(0,100),bty="n",ylab="% smolts captured at traps",xaxt="n",xlab="")
# axis(side=1,line=1,labels = years,at=1:data$Nyears, las=2, cex=.5)
# 
# # Moulin des Princes
# mcmc <- as.matrix(tmp[,paste0("p_B[",1:data$NBeau,"]")])    
# n <- t(apply(mcmc,2,quantile,probs=c(0.025, .5, 0.975)))*100
# segments(p,n[,"2.5%"], p,n[,"97.5%"], col=paste0(mycol[1]))
# #lines(n[,"50%"],lty=1,lwd=2,col=mycol[1],type="o")
# points(p,n[,"50%"],col=mycol[1],pch=21,bg=paste0(mycol[1]))
# 
# # Moulin du Leslé
# mcmc <- as.matrix(tmp[,paste0("p_ML[",3:data$NEu,"]")])    
# n <- t(apply(mcmc,2,quantile,probs=c(0.025, .5, 0.975)))*100
# n <- rbind(matrix(NA,2,3),n)
# segments(1:data$Nyears,n[,"2.5%"], 1:data$Nyears,n[,"97.5%"], col=paste0(mycol[2]))
# lines(n[,"50%"],lty=1,lwd=2,col=mycol[2],type="o")
# points(1:data$Nyears,n[,"50%"],col=mycol[2],pch=21,bg=paste0(mycol[2]))
# 
# legend("topright", legend=c("Moulin des Princes", "Moulin du Leslé"), col=mycol[1:2],lty=1,lwd=3,bty="n")
```

```{r}
##________________________BRESLE (starting in 1984)
site <- "Bresle"

years <- seq(1982, year, 1)
table <- array(, dim=c(length(years), 6))
colnames(table) <- c( "Smolt year","Smolts", 	"adults",	"global return rate (%)" ,	"1SW return rate (%)", "MSW return rate (%)")
rownames(table) <- years
smolt.years <- years
table[,1] <- smolt.years

## JUVENILES (1982 to now ; # /!\ NO CAPTURE IN 1988 to 1991 & 2001)
stade <- "smolt"
load(paste(wdir,"/",site,"/",stade,"/results/Results_",stade,"_",year,".RData",sep=""))
Nesc <- fit$median$Nesc # escapement from river
table[1:6,2] <- Nesc[1:6] # 1982 to 1987
table[11:19,2] <- Nesc[7:15] # 1992 to 2000
table[21:38,2] <- Nesc[16:33] # 2002 to 2019
table[40:nrow(table),2] <- Nesc[34:length(Nesc)] # 2002 to now

## ADULTS (1984 to now)
stade <- "adult"
load(paste(wdir,"/",site,"/",stade,"/results/Results_",stade,"_",year,".RData",sep=""))
n_1SW <- c(NA,NA,fit$median$n_1SW) # spawners 1SW
n_MSW <- c(NA,NA,fit$median$n_MSW) # spawners MSW

for (y in 1:(nrow(table))){
  table[y,3] <- n_1SW[y+1] + n_MSW[y+2] # Smolt 1+ become 1SW 1 years later / MSW 2 years later; /!\ NA reported if one of the two is missing!!!
  table[y,4] <- (table[y,3] / table[y,2])*100 
  table[y,5] <- (n_1SW[y+1]/ table[y,2])*100
  table[y,6] <- (n_MSW[y+2]/ table[y,2])*100
}

table[,2:3]<-round(table[,2:3],0)
table[,4:6]<-round(table[,4:6],2)

Avg <- apply(tail(table,10),2,mean,na.rm=TRUE)
table <- rbind(table,round(Avg,2))
rownames(table)[nrow(table)]<-"10yr avg"
table[nrow(table),1]<-"10yr avg"
#write.csv(round(table,2), file=paste('~/Documents/RESEARCH/PROJECTS/ORE/Abundance/CIEM/Table9_',site,"_",year,'.csv',sep=""))
con <- file(paste(wdir,"/",site,"/",stade,'/Table_ReturnRates_',site,'.csv',sep=""), open="wt")
# writeLines(paste("# Table 9 - juvenile and adult salmon  numbers (estim.) in-river return rate in the monitored rivers - ",site," (",year,")
#                   Nota : juvenile fish are smolts except in r. Nivelle which are parrs O+ (cohort parr 0+ = smolt.years -1). 
#                   Adult numbers refer to the smolt year N: runs of N+1 and N+2
#                   These are estimated trap-return numbers of wild fish except in 94-95 years in Nivelle when some stocked fish returned. 
#                  Stocking is considered to adjust numbers"
#                  ,sep=""), con)
write.csv( table, con, row.names = FALSE)
close(con)


# Plot of return rates
global <- as.numeric(table[-nrow(table),4])
plot(global,bty="n",ylab="Taux de retour (%)",xlab="Cohorte (smolt)",xaxt="n",ylim=c(0,30), type="b", main="Taux de retour (%)")
axis(side=1,line=0,labels = 1982:(year),at=1:length(years), las=2, cex=.5)
Osw <-as.numeric(table[-nrow(table),5])
points(Osw, type="b", col="darkblue")
legend("topright", legend=c("Global", "1SW"), fill=c("black","darkblue"), bty="n")


# Plot of return rates
global <- as.numeric(table[-nrow(table),4])/100
plot(log(global),bty="n",ylab="Taux de retour (log)",xlab="Cohorte (smolt)",xaxt="n",ylim=c(-5,0), type="b", main="Taux de retour (log)")
axis(side=1,line=0,labels = 1982:(year),at=1:length(years), las=2, cex=.5)
Osw <-as.numeric(table[-nrow(table),5])/100
points(log(Osw), type="b", col="darkblue")
legend("topright", legend=c("Global", "1SW"), fill=c("black","darkblue"), bty="n")


plot(NULL,bty="n",ylab="Taux de retour (%)",xlab="Cohorte (smolt)",xaxt="n",xlim=c(1,length(years)),ylim=c(0,6), main="Taux de retour des PHM")
axis(side=1,line=0,labels = 1982:(year),at=1:length(years), las=2, cex=.5)
Msw <-as.numeric(table[-nrow(table),6])
points(Msw, type="b", col="tomato")


plot(NULL,bty="n",ylab="Taux de retour (log)",xlab="Cohorte (smolt)",xaxt="n",xlim=c(1,length(years)),ylim=c(-10,0), main="Taux de retour des PHM (log)")
axis(side=1,line=0,labels = 1982:(year),at=1:length(years), las=2, cex=.5)
Msw <-log(as.numeric(table[-nrow(table),6])/100)
points(Msw, type="b", col="tomato")
```

