---
title: "Bilan_Scorff"
author: "Mathieu Buoro, Nicolas Jeannot & Etienne Prévost"
date: "3/20/2025"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
wdir <- "/media/HDD12To/mbuoro/ORE-DiaPFC/Abundance/Scorff"
setwd(wdir)

site <- "Scorff"
year <- 2024
years <- seq(1993, year, 1)

#COL <- c("yellowgreen","hotpink2","steelblue1","black")
mycol=c("#787878", "#1E90FF","#FF6A6A", "#a1dab4" )
#mycol <- paste0(COL, 50)
#mycol <- COL
##________________________SCORFF (starting in 1994)


```

### NOTA BENE

2021:\
- Séparer smolts 1+ vs 2+ 
- modele tacon: decoupler intercalibration vs modele d'estimation? + vérifier l'utilité des cut

2020:\
- IAS: pêche réalisée avec le Pulsium ; calibration en cours avec le Martin/pulsium\
- Smolt: estimation par classe d'âge? avec les proportions des âges / la série 2020\
- Adultes: Pièges non fonctionnels du 15 Mars au 11 Mai (COVID)\
- Recapture adultes hiver 2020: pêche à l'épuisette + pulsium intégré dans le modèle

### TABLEAU BILAN

Seules les valeurs médianes sont reportées. L'échappement correspond aux estimations après prise ne compte des sources de mortalités en rivière (pêche et naturelle).

```{r table, echo = FALSE}

table <- array(, dim=c(length(years), 10))
colnames(table) <- c( "Année","Tacon 0+","Smolts (tous)","Smolts 1+","Total retour", "1HM (retour)",	"PHM (retour)","Total échappement",	"1HM (échappement)",	"PHM (échappement)")
rownames(table) <- years
smolt.years <- years
table[,1] <- years


## PARR (from 1993 to now on)
stade <- "tacon"
nimble=FALSE
dir <-  paste(stade,sep="")
if (file.exists(dir)){
  load(paste(stade,"/results/Results_",stade,"_",year,".RData",sep=""))
  n_parr <- fit$median$ntot_Sc
  table[,2] <- round(n_parr,0) # 1995 to now
}



## SMOLTS (from 1995 to now on)
stade <- "smolt"
nimble=TRUE
dir <-  paste(stade,sep="")
if (file.exists(dir)){
  load(paste(stade,"/results/Results_",stade,"_",year,".RData",sep=""))
  
  if(nimble){
# Convert the mcmc.list to a matrix for easier manipulation
combined_chains <- as.matrix(fit)
# Extract column names that match the pattern "N\\[\\d+\\]" (i.e., "N[1]", "N[2]", ...)
param_names <- grep("^Ntot\\[\\d+\\]$", colnames(combined_chains), value = TRUE)
# Compute medians for the selected parameters
n_smolt <- apply(combined_chains[, param_names, drop = FALSE], 2, median)
  } else {
      n_smolt <- fit$median$Ntot # smolt numbers by year of migration
  }
  table[3:nrow(table),3] <- round(n_smolt,0) # 1995 to now
  
    if(nimble){
# Convert the mcmc.list to a matrix for easier manipulation
combined_chains <- as.matrix(fit)
# Extract column names that match the pattern "N\\[\\d+\\]" (i.e., "N[1]", "N[2]", ...)
param_names <- grep("^Nc\\[\\d+\\, 1]$", colnames(combined_chains), value = TRUE)
# Compute medians for the selected parameters
n_smolt <- apply(combined_chains[, param_names, drop = FALSE], 2, median)
  } else {
     n_smolt <- fit$median$Nc[,1] # smolt 1+ numbers by year of migration
  }
  table[3:nrow(table),4] <- round(n_smolt,0) # 1995 to now
}


## ADULTS (1984 to now)
stade <- "adult"
nimble=FALSE
dir <-  paste(stade,sep="")
if (file.exists(dir)){
  load(paste(stade,"/results/Results_",stade,"_",year,".RData",sep=""))
  
  # Avant pêche
  n_tot <-fit$median$n_tot # 1SW
  n_1SW <-fit$median$n_1SW # 1SW
  n_MSW <- fit$median$n_MSW #  MSW
  table[2:nrow(table),5] <- round(n_tot,0) # 1995 to now
  table[2:nrow(table),6] <- round(n_1SW,0) # 1995 to now
  table[2:nrow(table),7] <- round(n_MSW,0) # 1995 to now
  
  # Après mortalité en rivière
  e_tot <-fit$median$e_tot # 1SW
  e_1SW <-fit$median$e_1SW # 1SW
  e_MSW <- fit$median$e_MSW #  MSW
  table[2:nrow(table),8] <- round(e_tot,0) # 1995 to now
  table[2:nrow(table),9] <- round(e_1SW,0) # 1995 to now
  table[2:nrow(table),10] <- round(e_MSW,0) # 1995 to now
}


con <- file(paste0("Bilan_",site,"_",year,'.csv'), open="wt")
write.csv( table, con, row.names = FALSE)
close(con)

library(knitr)
kable(table, row.names = FALSE, caption = paste0("Tableau bilan pour le ",site,". Seules les valeurs médianes sont reportées. L'échappement corrspond aux estimations après prise ne compte des sources de mortalités en rivière (pêche et naturelle)"))

```

## ADULTES

## Nombre total de retour et échappement

```{r retour, echo=FALSE}
#### RETURNS

stade <- "adult"
dir <-  paste(wdir,"/",stade,sep="")
#if (file.exists(dir)){
# load dataset
load(paste(dir,"/data/data_",stade,"_",year,'.Rdata',sep="")) # chargement des données
load(paste0(dir,"/results/Results_",stade,"_",year,".RData"))
#}


tmp <- as.matrix(fit$sims.matrix)

#png(paste0(site,"/total_return.png"),width = 780, height = 480)
par(mfrow=c(1,1)) 

### Total number of returns
plot(NULL,xlim=c(1,data$Y),ylim=c(0,1500),bty="n",ylab="Effectif",xaxt="n",xlab="", main="Nombre total de retour de saumon sur le Scorff")
axis(side=1,line=1,labels = years[-1],at=1:data$Y, las=2, cex=.5)

# N total
mcmc <- as.matrix(tmp[,paste0("n_tot[",1:data$Y,"]")]) # 1984 to now)
n <- t(apply(mcmc,2,quantile,probs=c(0.025, .5, 0.975)))
segments(1:data$Y,n[,"2.5%"], 1:data$Y,n[,"97.5%"], col=paste0(mycol[3]))
lines(n[,"50%"],lty=1,lwd=2,col=mycol[3],type="o")
points(1:data$Y,n[,"50%"],col=mycol[3],pch=21,bg=paste0(mycol[3]))

#Escapement
mcmc <- as.matrix(tmp[,paste0("e_tot[",1:data$Y,"]")]) # 1984 to now)
e <- t(apply(mcmc,2,quantile,probs=c(0.025, .5, 0.975)))
segments(1:data$Y,e[,"2.5%"], 1:data$Y,e[,"97.5%"], col=paste0(mycol[4]))
lines(e[,"50%"],lty=1,lwd=2,col=mycol[4],type="o")
points(1:data$Y,e[,"50%"],col=mycol[4],pch=21,bg=paste0(mycol[4]))

abline(h=mean(n[,"50%"]), lty=2)
legend("topright", legend=c("Nombre total de retour", "Echappement (# retour après mortalité rivière)"), col=mycol[3:4],lty=1,lwd=2,bty="n")
#legend("topright", legend=c("Nombre total de retour"), col=mycol[3],lty=1,lwd=2,bty="n")
```

# Nombre total de retour par classe d'âge

```{r, echo=FALSE}


#plot(NULL,xlim=c(1,data$Y),ylim=c(0,1500),bty="n",ylab="Nombre total de retour",xaxt="n",xlab="")
#axis(side=1,line=1,labels = years[-1],at=1:data$Y, las=2, cex=.5)
#mycol=c("#787878", "#1E90FF", "#a1dab4", "#FF6A6A")

# 1SW
mcmc <- as.matrix(tmp[,paste0("n_1SW[",1:data$Y,"]")]) # 1984 to now)
n_1SW <- t(apply(mcmc,2,quantile,probs=c(0.025, .5, 0.975)))
plot(NULL,xlim=c(1,data$Y),ylim=c(0,1500),bty="n",ylab="Effectifs",xaxt="n",xlab="",main="Nombre total de retour 1HM")
axis(side=1,line=1,labels = years[-1],at=1:data$Y, las=2, cex=.5)
mycol=c("#787878", "#1E90FF", "#a1dab4", "#FF6A6A")
segments(1:data$Y,n_1SW[,"2.5%"], 1:data$Y,n_1SW[,"97.5%"], col=paste0(mycol[1]))
lines(n_1SW[,"50%"],lty=1,lwd=2,col=mycol[1],type="o")
points(1:data$Y,n_1SW[,"50%"],col=mycol[1],pch=21,bg=paste0(mycol[1]))
abline(h=mean(n_1SW[,"50%"], lty=2, col="lightgrey"))

# MSW
mcmc <- as.matrix(tmp[,paste0("n_MSW[",1:data$Y,"]")]) # 1984 to now)
n_MSW <- t(apply(mcmc,2,quantile,probs=c(0.025, .5, 0.975)))
plot(NULL,xlim=c(1,data$Y),ylim=c(0,300),bty="n",ylab="Effectifs",xaxt="n",xlab="",main="Nombre total de retour PHM")
axis(side=1,line=1,labels = years[-1],at=1:data$Y, las=2, cex=.5)
mycol=c("#787878", "#1E90FF", "#a1dab4", "#FF6A6A")
segments(1:data$Y,n_MSW[,"2.5%"], 1:data$Y,n_MSW[,"97.5%"], col=paste0(mycol[2]))
lines(n_MSW[,"50%"],lty=1,lwd=2,col=mycol[2],type="o")
points(1:data$Y,n_MSW[,"50%"],col=mycol[2],pch=21,bg=paste0(mycol[2]))
abline(h=mean(n_MSW[,"50%"], lty=3, col="lightgrey"))

#legend("topright", legend=c("1HM","PHM"), col=mycol[1:2],lty=1,lwd=2,bty="n")



#barplot(n_1SW[,"50%"])
#barplot(n_MSW[,"50%"], col=paste0(mycol[2]), border = paste0(mycol[2]),xaxt="n")
#axis(side=1,line=1,labels = 1994:2023,at=1:length(year), las=2, cex=.5)
#dev.off()


```

# Proportion Male/female

```{r, echo=FALSE}

#### CAPTURE AT MP ####
par(mfrow=c(1,1)) 
mycol=c("#787878", "#1E90FF", "#a1dab4", "#FF6A6A")
mcmc <- as.matrix(tmp[,paste0("p_male[",1:data$Y,",1]")]) # 
pmale_1SW <- t(apply(mcmc,2,quantile,probs=c(0.025, .5, 0.975)))*100
mcmc <- as.matrix(tmp[,paste0("p_male[",1:data$Y,",2]")]) # 
pmale_MSW <- t(apply(mcmc,2,quantile,probs=c(0.025, .5, 0.975)))*100
### Total number of returns
#png("report/total_return.png",width = 780, height = 480)
plot(NULL,xlim=c(1,data$Y),ylim=c(0,40),bty="n",ylab="Proportion de mâles (en %)",xaxt="n",xlab="",main="Proportion de mâles parmis les PHM")
axis(side=1,line=1,labels = years[-1],at=1:data$Y, las=2, cex=.5)

# N total
segments(1:data$Y,pmale_MSW[,"2.5%"], 1:data$Y,pmale_MSW[,"97.5%"], col=paste0(mycol[2]))
lines(pmale_MSW[,"50%"],lty=1,lwd=2,col=mycol[2],type="o")
points(1:data$Y,pmale_MSW[,"50%"],col=mycol[2],pch=21,bg=paste0(mycol[2]))

  df <- data.frame(x=1:data$Y, y= pmale_MSW[,"50%"])
  lw1 <- loess(y ~ x,span = 0.75, degree = 2, data=df)
  pred <- predict(lw1)
  lines(pred,col=mycol[2],lwd=2,lty=2)
 

  plot(NULL,xlim=c(1,data$Y),ylim=c(30,70),bty="n",ylab="Proportion de mâles (en %)",xaxt="n",xlab="",main="Proportion de mâles parmis les 1HM")
axis(side=1,line=1,labels = years[-1],at=1:data$Y, las=2, cex=.5)
 
# N total
segments(1:data$Y,pmale_1SW[,"2.5%"], 1:data$Y,pmale_1SW[,"97.5%"], col=paste0(mycol[1]))
lines(pmale_1SW[,"50%"],lty=1,lwd=2,col=mycol[1],type="o")
points(1:data$Y,pmale_1SW[,"50%"],col=mycol[1],pch=21,bg=paste0(mycol[1]))

  df <- data.frame(x=1:data$Y, y= pmale_1SW[,"50%"])
  lw1 <- loess(y ~ x,span = 0.75, degree = 2, data=df)
  pred <- predict(lw1)
  lines(pred,col=mycol[1],lwd=2,lty=2)
  
#legend("topright", legend=c("1HM", "PHM"), col=mycol[1:2],lty=1,lwd=3,bty="n")




```

# Proportion de saumon capturés au Moulin des Princes

```{r, echo=FALSE}

#### CAPTURE AT MP ####
par(mfrow=c(1,1)) 
mycol=c("#787878", "#1E90FF", "#a1dab4", "#FF6A6A")
mcmc <- as.matrix(tmp[,paste0("pi_MP[",1:data$Y,",1]")]) # 
piMP_1SW <- t(apply(mcmc,2,quantile,probs=c(0.025, .5, 0.975)))*100
mcmc <- as.matrix(tmp[,paste0("pi_MP[",1:data$Y,",2]")]) # 
piMP_MSW <- t(apply(mcmc,2,quantile,probs=c(0.025, .5, 0.975)))*100
### Total number of returns
#png("report/total_return.png",width = 780, height = 480)
plot(NULL,xlim=c(1,data$Y),ylim=c(0,100),bty="n",ylab="Proba de capture (en %)",xaxt="n",xlab="",main="Proba. de capture au Moulin des Princes")
axis(side=1,line=1,labels = years[-1],at=1:data$Y, las=2, cex=.5)

# N total
segments(1:data$Y,piMP_MSW[,"2.5%"], 1:data$Y,piMP_MSW[,"97.5%"], col=paste0(mycol[2]))
lines(piMP_MSW[,"50%"],lty=1,lwd=2,col=mycol[2],type="o")
points(1:data$Y,piMP_MSW[,"50%"],col=mycol[2],pch=21,bg=paste0(mycol[2]))

  df <- data.frame(x=1:data$Y, y= piMP_MSW[,"50%"])
  lw1 <- loess(y ~ x,span = 0.75, degree = 2, data=df)
  pred <- predict(lw1)
  lines(pred,col=mycol[2],lwd=2,lty=2)
  
# N total
segments(1:data$Y,piMP_1SW[,"2.5%"], 1:data$Y,piMP_1SW[,"97.5%"], col=paste0(mycol[1]))
lines(piMP_1SW[,"50%"],lty=1,lwd=2,col=mycol[1],type="o")
points(1:data$Y,piMP_1SW[,"50%"],col=mycol[1],pch=21,bg=paste0(mycol[1]))

  df <- data.frame(x=1:data$Y, y= piMP_1SW[,"50%"])
  lw1 <- loess(y ~ x,span = 0.75, degree = 2, data=df)
  pred <- predict(lw1)
  lines(pred,col=mycol[1],lwd=2,lty=2)
  
legend("topright", legend=c("1HM", "PHM"), col=mycol[1:2],lty=1,lwd=3,bty="n")




```

<!-- # Taux d'exploitation  -->

<!-- Ici, les taux d'exploitation sont estimés par classe d'âge et suivant si les individus ont été marqués préalablement au Moulin des Princes. On observe que les individus marqués ont une probabilité d'être capturés à la ligne inférieure à ceux non marqués. -->

<!-- ```{r, echo=FALSE} -->

<!-- ## a: sea age;  -->

<!-- ##    1-1SW (Grisle),  -->

<!-- ##    2-MSW (salmon) -->

<!-- ## u: effect of being marked -->

<!-- ##    1 - marked -->

<!-- ##    2 - unmarked -->

<!-- ################################################################################ -->

<!-- ## PROBABILITY DISTRIBUTIONS -->

<!-- ## ------------------------- -->

<!-- ## pi_MP94[a]:probability to be captured at Moulin des Princes given sea age for 1994  -->

<!-- ## pi_MP[t,a]:annual probability to be captured at Moulin des Princes given sea age -->

<!-- ## pi_D_1SW[t,a]: annual probability for a marked 1SW to die from cause other than fishing given marking -->

<!-- ## pi_D_MSW[t,a]: annual probability for a marked MSW to die from cause other than fishing given marking -->

<!-- ## pi_Dum[t,a]: annual probability for a unmarked fish to die from cause other than fishing given sea age -->

<!-- ## pi_oD: probability to recover a fish that die from other cause than fishing -->

<!-- ## pi_F_1SW[t,a]: annual probability of a 1SW to be captured by fishing given marking -->

<!-- ## pi_F_MSW[t,a]: annual probability of a MSW to be captured by fishing given marking  -->

<!-- ## pi_oF[t,a]: annual probability to recover a caught fish (exploitation). From 1994 to 2002. -->

<!-- ## pi_R[t,a]: annual probability to be captured during or after reproduction given sea age -->

<!-- ####################################################################################   -->

<!-- par(mfrow=c(1,2))  -->

<!-- #### 1SW #### -->

<!-- #piF_1SW[10,1] <- 0 # No exploitation allowed on 1SW in 2003 -->

<!-- #piF_1SW[10,2] <- 0 # No exploitation allowed on 1SW in 2003  -->

<!-- mcmc <- as.matrix(tmp[,paste0("piF_1SW[",c(1:9,11:data$Y),",1]")]) #  -->

<!-- piF_1SWm <- t(apply(mcmc,2,quantile,probs=c(0.025, .5, 0.975)))*100 -->

<!-- piF_1SWm <- rbind(piF_1SWm[1:9,], c(0,0,0),piF_1SWm[10:(data$Y-1),]) -->

<!-- mcmc <- as.matrix(tmp[,paste0("piF_1SW[",c(1:9,11:data$Y),",2]")]) #  -->

<!-- piF_1SWum <- t(apply(mcmc,2,quantile,probs=c(0.025, .5, 0.975)))*100 -->

<!-- piF_1SWum <- rbind(piF_1SWum[1:9,], c(0,0,0),piF_1SWum[10:(data$Y-1),]) -->

<!-- ### Total number of returns -->

<!-- #png("report/total_return.png",width = 780, height = 480) -->

<!-- plot(NULL,xlim=c(1,data$Y),ylim=c(0,50),bty="n",ylab="% 1SW captured by fishing",xaxt="n",xlab="")#, main="% 1SW to be captured by fishing") -->

<!-- axis(side=1,line=1,labels = years[-1],at=1:data$Y, las=2, cex=.5) -->

<!-- # N total -->

<!-- segments(1:data$Y,piF_1SWm[,"2.5%"], 1:data$Y,piF_1SWm[,"97.5%"], col=paste0(mycol[4])) -->

<!-- lines(piF_1SWm[,"50%"],lty=1,lwd=2,col=mycol[4],type="o") -->

<!-- points(1:data$Y,piF_1SWm[,"50%"],col=mycol[4],pch=21,bg=paste0(mycol[4])) -->

<!-- # N total -->

<!-- segments(1:data$Y,piF_1SWum[,"2.5%"], 1:data$Y,piF_1SWum[,"97.5%"], col=paste0(mycol[3])) -->

<!-- lines(piF_1SWum[,"50%"],lty=1,lwd=2,col=mycol[3],type="o") -->

<!-- points(1:data$Y,piF_1SWum[,"50%"],col=mycol[3],pch=21,bg=paste0(mycol[3])) -->

<!-- legend("topright", legend=c("Unmarked", "Marked"), col=mycol[3:4],lty=1,lwd=3,bty="n") -->

<!-- #### MSW #### -->

<!-- mcmc <- as.matrix(tmp[,paste0("piF_MSW[",1:data$Y,",1]")]) #  -->

<!-- piF_MSWm <- t(apply(mcmc,2,quantile,probs=c(0.025, .5, 0.975)))*100 -->

<!-- mcmc <- as.matrix(tmp[,paste0("piF_MSW[",1:data$Y,",2]")]) #  -->

<!-- piF_MSWum <- t(apply(mcmc,2,quantile,probs=c(0.025, .5, 0.975)))*100 -->

<!-- ### Total number of returns -->

<!-- #png("report/total_return.png",width = 780, height = 480) -->

<!-- plot(NULL,xlim=c(1,data$Y),ylim=c(0,50),bty="n",ylab="% MSW captured by fishing",xaxt="n",xlab="")#,main="% MSW to be captured by fishing") -->

<!-- axis(side=1,line=1,labels = years[-1],at=1:data$Y, las=2, cex=.5) -->

<!-- # N total -->

<!-- segments(1:data$Y,piF_MSWm[,"2.5%"], 1:data$Y,piF_MSWm[,"97.5%"], col=paste0(mycol[4])) -->

<!-- lines(piF_MSWm[,"50%"],lty=1,lwd=2,col=mycol[4],type="o") -->

<!-- points(1:data$Y,piF_MSWm[,"50%"],col=mycol[4],pch=21,bg=paste0(mycol[4])) -->

<!-- # N total -->

<!-- segments(1:data$Y,piF_MSWum[,"2.5%"], 1:data$Y,piF_MSWum[,"97.5%"], col=paste0(mycol[3])) -->

<!-- lines(piF_MSWum[,"50%"],lty=1,lwd=2,col=mycol[3],type="o") -->

<!-- points(1:data$Y,piF_MSWum[,"50%"],col=mycol[3],pch=21,bg=paste0(mycol[3])) -->

<!-- legend("topright", legend=c("Unmarked", "Marked"), col=mycol[3:4],lty=1,lwd=3,bty="n") -->

<!-- ``` -->

<!-- ```{r, echo=FALSE} -->

<!-- #### PROB. DEAD #### -->

<!-- par(mfrow=c(1,2))  -->

<!-- #### 1SW #### -->

<!-- mcmc <- as.matrix(tmp[,paste0("piD_1SW[",1:data$Y,",1]")]) #  -->

<!-- piD_1SWm <- t(apply(mcmc,2,quantile,probs=c(0.025, .5, 0.975)))*100 -->

<!-- mcmc <- as.matrix(tmp[,paste0("piD_1SW[",1:data$Y,",2]")]) #  -->

<!-- piD_1SWum <- t(apply(mcmc,2,quantile,probs=c(0.025, .5, 0.975)))*100 -->

<!-- ### Total number of returns -->

<!-- #png("report/total_return.png",width = 780, height = 480) -->

<!-- plot(NULL,xlim=c(1,data$Y),ylim=c(0,50),bty="n",ylab="% 1SW dead from cause other than fishing",xaxt="n",xlab="")#, main="% 1SW to be captured by fishing") -->

<!-- axis(side=1,line=1,labels = years[-1],at=1:data$Y, las=2, cex=.5) -->

<!-- # N total -->

<!-- segments(1:data$Y,piD_1SWm[,"2.5%"], 1:data$Y,piD_1SWm[,"97.5%"], col=paste0(mycol[4])) -->

<!-- lines(piD_1SWm[,"50%"],lty=1,lwd=2,col=mycol[4],type="o") -->

<!-- points(1:data$Y,piD_1SWm[,"50%"],col=mycol[4],pch=21,bg=paste0(mycol[4])) -->

<!-- # N total -->

<!-- segments(1:data$Y,piD_1SWum[,"2.5%"], 1:data$Y,piD_1SWum[,"97.5%"], col=paste0(mycol[3])) -->

<!-- lines(piD_1SWum[,"50%"],lty=1,lwd=2,col=mycol[3],type="o") -->

<!-- points(1:data$Y,piD_1SWum[,"50%"],col=mycol[3],pch=21,bg=paste0(mycol[3])) -->

<!-- legend("topright", legend=c("Unmarked", "Marked"), col=mycol[3:4],lty=1,lwd=3,bty="n") -->

<!-- #### MSW #### -->

<!-- mcmc <- as.matrix(tmp[,paste0("piD_MSW[",1:data$Y,",1]")]) #  -->

<!-- piD_MSWm <- t(apply(mcmc,2,quantile,probs=c(0.025, .5, 0.975)))*100 -->

<!-- mcmc <- as.matrix(tmp[,paste0("piD_MSW[",1:data$Y,",2]")]) #  -->

<!-- piD_MSWum <- t(apply(mcmc,2,quantile,probs=c(0.025, .5, 0.975)))*100 -->

<!-- ### Total number of returns -->

<!-- #png("report/total_return.png",width = 780, height = 480) -->

<!-- plot(NULL,xlim=c(1,data$Y),ylim=c(0,50),bty="n",ylab="% MSW dead from cause other than fishing",xaxt="n",xlab="")#,main="% MSW to be captured by fishing") -->

<!-- axis(side=1,line=1,labels = years[-1],at=1:data$Y, las=2, cex=.5) -->

<!-- # N total -->

<!-- segments(1:data$Y,piD_MSWm[,"2.5%"], 1:data$Y,piD_MSWm[,"97.5%"], col=paste0(mycol[4])) -->

<!-- lines(piD_MSWm[,"50%"],lty=1,lwd=2,col=mycol[4],type="o") -->

<!-- points(1:data$Y,piD_MSWm[,"50%"],col=mycol[4],pch=21,bg=paste0(mycol[4])) -->

<!-- # N total -->

<!-- segments(1:data$Y,piD_MSWum[,"2.5%"], 1:data$Y,piD_MSWum[,"97.5%"], col=paste0(mycol[3])) -->

<!-- lines(piD_MSWum[,"50%"],lty=1,lwd=2,col=mycol[3],type="o") -->

<!-- points(1:data$Y,piD_MSWum[,"50%"],col=mycol[3],pch=21,bg=paste0(mycol[3])) -->

<!-- legend("topright", legend=c("Unmarked", "Marked"), col=mycol[3:4],lty=1,lwd=3,bty="n") -->

<!-- ``` -->

# Probabilities to die from other cause than fishing (time, mark status and sea age dependent)

```{r, echo=FALSE}

#### CAPTURE AT MP ####
par(mfrow=c(1,1)) 
mycol=c("#787878", "#1E90FF", "#a1dab4", "#FF6A6A")
mcmc <- as.matrix(tmp[,paste0("piD_1SW[",1:data$Y,",1]")]) # 
piD_1SWm <- t(apply(mcmc,2,quantile,probs=c(0.025, .5, 0.975)))*100
mcmc <- as.matrix(tmp[,paste0("piD_1SW[",1:data$Y,",2]")]) # 
piD_1SWum <- t(apply(mcmc,2,quantile,probs=c(0.025, .5, 0.975)))*100

mcmc <- as.matrix(tmp[,paste0("piD_MSW[",1:data$Y,",1]")]) # 
piD_MSWm <- t(apply(mcmc,2,quantile,probs=c(0.025, .5, 0.975)))*100
mcmc <- as.matrix(tmp[,paste0("piD_MSW[",1:data$Y,",2]")]) # 
piD_MSWum <- t(apply(mcmc,2,quantile,probs=c(0.025, .5, 0.975)))*100


### Total number of returns
#png("report/total_return.png",width = 780, height = 480)
plot(NULL,xlim=c(1,data$Y),ylim=c(0,100),bty="n",ylab="Proba de mortalité (en %)",xaxt="n",xlab="",main="Proba. de mortalité (hors exploitation)")
axis(side=1,line=1,labels = years[-1],at=1:data$Y, las=2, cex=.5)

# N total
segments(1:data$Y,piD_1SWm[,"2.5%"], 1:data$Y,piD_1SWm[,"97.5%"], col=paste0(mycol[2]))
lines(piD_1SWm[,"50%"],lty=1,lwd=2,col=mycol[2],type="o")
points(1:data$Y,piD_1SWm[,"50%"],col=mycol[2],pch=21,bg=paste0(mycol[2]))

  df <- data.frame(x=1:data$Y, y= piD_1SWm[,"50%"])
  lw1 <- loess(y ~ x,span = 0.75, degree = 2, data=df)
  pred <- predict(lw1)
  lines(pred,col=mycol[2],lwd=2,lty=2)
  
# N total
# segments(1:data$Y,piD_1SWum[,"2.5%"], 1:data$Y,piD_1SWum[,"97.5%"], col=paste0(mycol[1]))
# lines(piD_1SWum[,"50%"],lty=1,lwd=2,col=mycol[1],type="o")
# points(1:data$Y,piD_1SWum[,"50%"],col=mycol[1],pch=21,bg=paste0(mycol[1]))
# 
#   df <- data.frame(x=1:data$Y, y= piD_1SWum[,"50%"])
#   lw1 <- loess(y ~ x,span = 0.75, degree = 2, data=df)
#   pred <- predict(lw1)
#   lines(pred,col=mycol[1],lwd=2,lty=2)
#   
#  legend("topright", legend=c("marked", "unmarked"), col=mycol[1:2],lty=1,lwd=3,bty="n")
  
  
  # MSW
#plot(NULL,xlim=c(1,data$Y),ylim=c(0,100),bty="n",ylab="Proba de mortalité (en %)",xaxt="n",xlab="",main="Proba. de mortalité des PHM")
#axis(side=1,line=1,labels = years[-1],at=1:data$Y, las=2, cex=.5)

# segments(1:data$Y,piD_MSWm[,"2.5%"], 1:data$Y,piD_MSWm[,"97.5%"], col=paste0(mycol[3]))
# lines(piD_MSWm[,"50%"],lty=1,lwd=2,col=mycol[3],type="o")
# points(1:data$Y,piD_MSWm[,"50%"],col=mycol[3],pch=21,bg=paste0(mycol[3]))
# 
#   df <- data.frame(x=1:data$Y, y= piD_MSWm[,"50%"])
#   lw1 <- loess(y ~ x,span = 0.75, degree = 2, data=df)
#   pred <- predict(lw1)
#   lines(pred,col=mycol[3],lwd=2,lty=2)
  
# N total
segments(1:data$Y,piD_MSWum[,"2.5%"], 1:data$Y,piD_MSWum[,"97.5%"], col=paste0(mycol[4]))
lines(piD_MSWum[,"50%"],lty=1,lwd=2,col=mycol[4],type="o")
points(1:data$Y,piD_MSWum[,"50%"],col=mycol[4],pch=21,bg=paste0(mycol[4]))

  df <- data.frame(x=1:data$Y, y= piD_MSWum[,"50%"])
  lw1 <- loess(y ~ x,span = 0.75, degree = 2, data=df)
  pred <- predict(lw1)
  lines(pred,col=mycol[4],lwd=2,lty=2)
  
#legend("topright", legend=c("marked", "unmarked"), col=mycol[1:2],lty=1,lwd=3,bty="n")

legend("topright", legend=c("1HM", "PHM"), col=c(mycol[2],mycol[4]),lty=1,lwd=3,bty="n")

tmp <- data.frame(Years=1993:(year-1), MSW=piD_MSWum[,"50%"], OneSW=piD_1SWum[,"50%"])
library(knitr)
kable(tmp, row.names = FALSE, caption = paste0("Tableau bilan mortalité naturelle (en %) pour le ",site,". Seules les valeurs médianes sont reportées"))


```

# SMOLTS

## Nombre de smolts estimés

```{r smolt, echo=FALSE}

stade <- "smolt"
nimble=TRUE
#dir <-  paste(wdir,site,"/",stade,sep="")
#if (file.exists(dir)){
# load dataset
load(paste(stade,"/data/data_",stade,"_",year,'.Rdata',sep="")) # chargement des données
load(paste0(stade,"/results/Results_",stade,"_",year,".RData"))
#}

if(nimble){
  tmp <- as.matrix(fit)
}else{
  tmp <- as.matrix(fit$sims.matrix)
}


#png(paste0(site,"/total_return.png"),width = 780, height = 480)
par(mfrow=c(1,1)) 

### Total number of returns
plot(NULL,xlim=c(1,data$Nyears),ylim=c(0,15000),bty="n",ylab="Nombre total de smolts",xaxt="n",xlab="Année de migration")
axis(side=1,line=1,labels = years[-c(1,2)],at=1:data$Nyears, las=2, cex.axis=.6)

# N total
mcmc <- as.matrix(tmp[,paste0("Ntot[",1:data$Nyears,"]")])    
n <- t(apply(mcmc,2,quantile,probs=c(0.025, .5, 0.975)))
segments(1:data$Nyears,n[,"2.5%"], 1:data$Nyears,n[,"97.5%"], col=paste0(mycol[1]))
lines(n[,"50%"],lty=1,lwd=2,col=mycol[1],type="o")
points(1:data$Nyears,n[,"50%"],col=mycol[1],pch=21,bg=paste0(mycol[1]))
abline(h=mean(n[,"50%"], lty=2, col="lightgrey"))
# # Escapment
# mcmc <- as.matrix(tmp[,paste0("Nesc[",1:data$Nyears,"]")])    
# n <- t(apply(mcmc,2,quantile,probs=c(0.025, .5, 0.975)))
# segments(1:data$Nyears,n[,"2.5%"], 1:data$Nyears,n[,"97.5%"], col=paste0(mycol[2]))
# lines(n[,"50%"],lty=1,lwd=2,col=mycol[2],type="o")
# points(1:data$Nyears,n[,"50%"],col=mycol[2],pch=21,bg=paste0(mycol[2]))

#legend("topright", legend=c("Nombre total de smolts", "Echappement"), col=mycol[1:2],lty=1,lwd=2,bty="n")


par(mfrow=c(1,1)) 

### Total number of returns
plot(NULL,xlim=c(1,data$Nyears),ylim=c(0,15000),bty="n",ylab="Nombre total de smolts",xaxt="n",xlab="Cohorte")
axis(side=1,line=1,labels = 1994:(year-1),at=1:data$Nyears, las=2, cex.axis=.6)

# N total
mcmc <- as.matrix(tmp[,paste0("N[",1:data$Nyears,"]")])    
n <- t(apply(mcmc,2,quantile,probs=c(0.025, .5, 0.975)))
segments(1:data$Nyears,n[,"2.5%"], 1:data$Nyears,n[,"97.5%"], col=paste0(mycol[1]))
lines(n[,"50%"],lty=1,lwd=2,col=mycol[1],type="o")
points(1:data$Nyears,n[,"50%"],col=mycol[1],pch=21,bg=paste0(mycol[1]))
abline(h=mean(n[,"50%"], lty=2, col="lightgrey"))


par(mfrow=c(1,1)) 

### Total number of returns
plot(NULL,xlim=c(1,data$Nyears),ylim=c(0,1),bty="n",ylab="Proportion de smolts 1+",xaxt="n",xlab=" Cohorte")
axis(side=1,line=1,labels = years[-c(1,2)],at=1:data$Nyears, las=2, cex.axis=.6)
# N total
mcmc <- as.matrix(tmp[,paste0("p1c[",1:data$Nyears,"]")])    
n <- t(apply(mcmc,2,quantile,probs=c(0.025, .5, 0.975)))
segments(1:data$Nyears,n[,"2.5%"], 1:data$Nyears,n[,"97.5%"], col=paste0(mycol[1]))
lines(n[,"50%"],lty=1,lwd=2,col=mycol[1],type="o")
points(1:data$Nyears,n[,"50%"],col=mycol[1],pch=21,bg=paste0(mycol[1]))
abline(h=mean(n[,"50%"], lty=2, col="lightgrey"))

```

```{r capt_smolt, echo=FALSE}
par(mfrow=c(1,1)) 

### Total number of returns
plot(NULL,xlim=c(1,data$Nyears),ylim=c(0,80),bty="n",ylab="% smolts capturé aux pièges",xaxt="n",xlab="Année de migration")
axis(side=1,line=1,labels = 1995:year,at=1:data$Nyears, las=2, cex.axis=.7)

# Moulin des Princes
mcmc <- as.matrix(tmp[,paste0("p_MP[",1:data$Nyears,"]")])    
n <- t(apply(mcmc,2,quantile,probs=c(0.025, .5, 0.975)))*100
segments(1:data$Nyears,n[,"2.5%"], 1:data$Nyears,n[,"97.5%"], col=paste0(mycol[1]))
lines(n[,"50%"],lty=1,lwd=2,col=mycol[1],type="o")
points(1:data$Nyears,n[,"50%"],col=mycol[1],pch=21,bg=paste0(mycol[1]))

# Moulin du Leslé
mcmc <- as.matrix(tmp[,paste0("p_ML[",3:data$Nyears,"]")])    
n <- t(apply(mcmc,2,quantile,probs=c(0.025, .5, 0.975)))*100
n <- rbind(matrix(NA,2,3),n)
segments(1:data$Nyears,n[,"2.5%"], 1:data$Nyears,n[,"97.5%"], col=paste0(mycol[2]))
lines(n[,"50%"],lty=1,lwd=2,col=mycol[2],type="o")
points(1:data$Nyears,n[,"50%"],col=mycol[2],pch=21,bg=paste0(mycol[2]))

legend("topright", legend=c("Moulin des Princes", "Moulin du Leslé"), col=mycol[1:2],lty=1,lwd=3,bty="n")
```

```{r env, echo=FALSE}

stade <- "smolt"
dir <-  paste(wdir,"/",stade,sep="")
#if (file.exists(dir)){
# load dataset
#load(paste(stade,"/data/data_",stade,"_",year,'.Rdata',sep="")) # chargement des données
#load(paste0(stade,"/results/Results_",stade,"_",year,".RData"))
#}

Q <- read.table(paste(dir,"/data/data_flow.txt",sep=""),header = TRUE, check.names=FALSE,comment.char = "#",colClasses="character")
Q <- as.matrix(Q);mode(Q)<- "numeric"


#png(paste0(site,"/total_return.png"),width = 780, height = 480)
par(mfrow=c(1,1)) 

### Total number of returns
plot(NULL,xlim=c(1,data$Nyears),ylim=c(0,20),bty="n",ylab="Débit moyen du 1er Avril au 10 Mai",xaxt="n",xlab="")
axis(side=1,line=1,labels = years[-c(1,2)],at=1:data$Nyears, las=2, cex=.5)

lines(Q[,1],lty=1,lwd=2,col="steelblue1",type="o")

#legend("topright", legend=c("Moulin des Princes", "Moulin du Leslé"),col=mycol[1:2],lty=1,lwd=2,bty="n")

```

# TACON

```{r parr, echo=FALSE}

# TACONS

stade <- "tacon"
#dir <-  paste(wdir,site,"/",stade,sep="")
#if (file.exists(dir)){
# load dataset
load(paste(stade,"/data/data_",stade,"_",year,'.Rdata',sep="")) # chargement des données
load(paste0(stade,"/results/Results_",stade,"_",year,".RData"))
#}


tmp <- as.matrix(fit$sims.matrix)

#png(paste0(site,"/total_return.png"),width = 780, height = 480)
par(mfrow=c(1,1)) 

### Total number of returns
plot(NULL,xlim=c(1,data$Nyear),ylim=c(0,80000),bty="n",ylab="Effectif",xaxt="n",xlab="Cohorte", main="Nombre total de tacons 0+")
axis(side=1,line=1,labels = years,at=1:data$Nyear, las=2, cex.axis=.7)

# N total
mcmc <- as.matrix(tmp[,paste0("ntot_Sc[",1:data$Nyear,"]")])    
n <- t(apply(mcmc,2,quantile,probs=c(0.025, .5, 0.975)))
segments(1:data$Nyear,n[,"2.5%"], 1:data$Nyear,n[,"97.5%"], col="black")
lines(n[,"50%"],lty=1,lwd=2,col=mycol[1],type="o")
points(1:data$Nyear,n[,"50%"],col="black",pch=21,bg="black")
abline(h=mean(n[,"50%"], lty=2, col="lightgrey"))

```

1.  Relation Parr-Smolt

```{r parr-smolt survival, echo=FALSE}

#setwd("/media/HDD12To/mbuoro/ORE-DiaPFC/Abundance/Scorff")


stade <- "smolt" # 1995:now
nimble=TRUE
#dir <-  paste(wdir,site,"/",stade,sep="")
#if (file.exists(dir)){
# load dataset
load(paste(stade,"/data/data_",stade,"_",year,'.Rdata',sep="")) # chargement des données
load(paste0(stade,"/results/Results_",stade,"_",year,".RData"))
if(nimble){
  tmp <- as.matrix(fit)
}else{
  tmp <- as.matrix(fit$sims.matrix)
}

#mcmc <- as.matrix(tmp[,paste0("Ntot[",1:data$Nyears,"]")])  
mcmc <- as.matrix(tmp[,paste0("Nc[",1:data$Nyears,", 1]")]) # 1995 
smolt <- t(apply(mcmc,2,quantile,probs=c(0.025, .5, 0.975)))

stade <- "tacon" # 1993 to now
load(paste(stade,"/data/data_",stade,"_",year,'.Rdata',sep="")) 
load(paste0(stade,"/results/Results_",stade,"_",year,".RData"))
parr <- as.matrix(fit$sims.matrix)
mcmc <- as.matrix(parr[,paste0("ntot_Sc[",1:data$Nyear,"]")]) 
parr <- t(apply(mcmc,2,quantile,probs=c(0.025, .5, 0.975)))



labels=1995:(year-1)
boxes <- sapply(nchar(labels), function(n) 
  paste(rep("\U2588", n), collapse=""))


#png(paste0(site,"/total_return.png"),width = 780, height = 480)
par(mfrow=c(1,1)) 

# debut des smolts en 1995 et tacon en 1993
ratio <- smolt[1:nrow(smolt),"50%"]/parr[2:(nrow(parr)-1),"50%"]
plot(ratio,bty="n",ylab="Ratio Smolts 1+/Tacons 0+",xlab="Cohorte (tacons)",xaxt="n",ylim=c(0,1))
axis(side=1,line=0,labels = 1994:(year-1),at=1:(length(years)-2), las=2, cex=.5)

  df <- data.frame(x=1994:(year-1), y= ratio)
  lw1 <- loess(y ~ x,span = 0.75, degree = 2, data=df)
  pred <- predict(lw1)
  lines(pred,col=1,lwd=2,lty=1)
  
  
  

### Total number of returns
#plot(NULL,xlim=c(0,50000),ylim=c(0,20000),bty="n",ylab="Smolt 1+",xlab="Tacon 0+")
#axis(side=1,line=1,labels = years,at=1:data$Nyear, las=2, cex=.5)
#points(r[2:28,"50%"],smolt[1:27,"50%"],col=mycol[1],pch=21,bg=paste0(mycol[1]))
#segments(ratio[1:29,"2.5%"],smolt[1:29,"50%"],ratio[1:29,"97.5%"],smolt[1:29,"50%"], col=paste0(mycol[1]))
#segments(ratio[1:29,"50%"],smolt[1:29,"2.5%"],ratio[1:29,"50%"],smolt[1:29,"97.5%"], col=paste0(mycol[1]))
#text(r[2:28,"50%"],smolt[1:27,"50%"],labels=boxes, col="#CCCCCC99")
#text(ratio[1:29,"50%"],smolt[1:29,"50%"],labels = years, cex=.7)




# plot(NULL,xlim=c(1,28),ylim=c(0,1),bty="n",ylab="Survie tacon - Smolt",xlab="Cohorte",xaxt="n")
# axis(side=1,line=0,labels = labels,at=1:27, las=2, cex.axis=.7)
# size <- r[2:28,"50%"]/10000
# points(1:27,smolt[1:27,"50%"]/r[2:28,"50%"],col=mycol[1],pch=21, bg=24,lwd=.5,cex=size)


# library(plotly)
# 
# df <- data.frame(parr=r[2:28,"50%"],smolt=smolt[1:27,"50%"])
# df$surv <- df$smolt/df$parr
# df$year <- 1995:2021
# 
# fig <- plot_ly(df, x = ~year, y = ~surv, text = ~year, type = 'scatter', mode = 'markers', color = ~parr, colors = 'Reds',marker = list(size = ~parr/1000, opacity = 0.5))
# fig <- fig %>% layout(title = 'Survie Tacon-Smolt',
#          xaxis = list(showgrid = FALSE),
#          yaxis = list(showgrid = FALSE))
# 
# fig
```

```{r return}
site <- "Scorff"
dir <-  paste(wdir,"/",sep="")
years <- seq(1994, year, 1)
table <- array(, dim=c(length(years), 6))
colnames(table) <- c( "Smolt year","Smolts", 	"adults",	"global return rate (%)" ,	"1SW return rate (%)", "MSW return rate (%)")
rownames(table) <- years
smolt.years <- years
table[,1] <- smolt.years

## JUVENILES from 1995 to now on
stade <- "smolt"
nimble=TRUE
load(paste(dir,"/",stade,"/results/Results_",stade,"_",year,".RData",sep=""))
 if(nimble){
# Convert the mcmc.list to a matrix for easier manipulation
combined_chains <- as.matrix(fit)
# Extract column names that match the pattern "N\\[\\d+\\]" (i.e., "N[1]", "N[2]", ...)
param_names <- grep("^Nesc\\[\\d+\\]$", colnames(combined_chains), value = TRUE)
# Compute medians for the selected parameters
Nesc <- apply(combined_chains[, param_names, drop = FALSE], 2, median)
  } else {
      Nesc <- fit$median$Nesc # escapement from river
  }

table[2:nrow(table),2] <- Nesc # 1995 to now



## ADULTS (1984 to now)
stade <- "adult"
load(paste(dir,"/",stade,"/results/Results_",stade,"_",year,".RData",sep=""))
n_1SW <- c(fit$median$n_1SW) 
n_MSW <- c(fit$median$n_MSW)

for (y in 1:(nrow(table))){
  
  table[y,5] <- (n_1SW[y+1]/ table[y,2])*100
  table[y,6] <- (n_MSW[y+2]/ table[y,2])*100
  
  if (is.na(n_1SW[y+1]) | is.na(n_MSW[y+2]) | is.na(table[y,2])) next;
  table[y,3] <- n_1SW[y+1] + n_MSW[y+2] # Smolt 1+ become 1SW 1 years later / MSW 2 years later; /!\ NA reported if one of the two is missing!!!
  table[y,4] <- (table[y,3] / table[y,2])*100 
}

table[,2:3]<-round(table[,2:3],0)
table[,4:6]<-round(table[,4:6],2)

Avg <- apply(tail(table,10),2,mean,na.rm=TRUE)
table <- rbind(table,round(Avg,2))
rownames(table)[nrow(table)]<-"10yr avg"
table[nrow(table),1]<-"10yr avg"
#write.csv(round(table,2), file=paste('~/Documents/RESEARCH/PROJECTS/ORE/Abundance/CIEM/Table9_',site,"_",year,'.csv',sep=""))
con <- file(paste('Table_ReturnRates_',site,'.csv',sep=""), open="wt")
# writeLines(paste("# Table 9 - juvenile and adult salmon  numbers (estim.) in-river return rate in the monitored rivers - ",site," (",year,")
#                   Nota : juvenile fish are smolts except in r. Nivelle which are parrs O+ (cohort parr 0+ = smolt.years -1). 
#                   Adult numbers refer to the smolt year N: runs of N+1 and N+2
#                   These are estimated trap-return numbers of wild fish except in 94-95 years in Nivelle when some stocked fish returned. 
#                  Stocking is considered to adjust numbers"
#                  ,sep=""), con)
write.csv( table, con, row.names = FALSE)
close(con)

# Plot of return rates
global <- as.numeric(table[-nrow(table),4])
plot(global,bty="n",ylab="Taux de retour (%)",xlab="Cohorte (smolt)",xaxt="n",ylim=c(0,30), type="b", main="Taux de retour (%)")
axis(side=1,line=0,labels = 1994:(year),at=1:length(years), las=2, cex=.5)
Osw <-as.numeric(table[-nrow(table),5])
points(Osw, type="b", col="darkblue")
legend("topright", legend=c("Global", "1SW"), fill=c("black","darkblue"), bty="n")


# Plot of return rates
global <- as.numeric(table[-nrow(table),4])/100
plot(log(global),bty="n",ylab="Taux de retour (log)",xlab="Cohorte (smolt)",xaxt="n",ylim=c(-5,0), type="b", main="Taux de retour (log)")
axis(side=1,line=0,labels = 1994:(year),at=1:length(years), las=2, cex=.5)
Osw <-as.numeric(table[-nrow(table),5])/100
points(log(Osw), type="b", col="darkblue")
legend("topright", legend=c("Global", "1SW"), fill=c("black","darkblue"), bty="n")


plot(NULL,bty="n",ylab="Taux de retour (%)",xlab="Cohorte (smolt)",xaxt="n",xlim=c(1,length(years)),ylim=c(0,6), main="Taux de retour des PHM")
axis(side=1,line=0,labels = 1994:(year),at=1:length(years), las=2, cex=.5)
Msw <-as.numeric(table[-nrow(table),6])
points(Msw, type="b", col="tomato")


plot(NULL,bty="n",ylab="Taux de retour (log)",xlab="Cohorte (smolt)",xaxt="n",xlim=c(1,length(years)),ylim=c(-10,0), main="Taux de retour des PHM (log)")
axis(side=1,line=0,labels = 1994:(year),at=1:length(years), las=2, cex=.5)
Msw <-log(as.numeric(table[-nrow(table),6])/100)
points(Msw, type="b", col="tomato")


```


#Stock : number of anadromous adults escaped (available for reproduction) #Recruitment: number of parr 0+

<!-- ```{r SR, echo=FALSE} -->

<!-- stade <- "adult" -->

<!-- load(paste(stade,"/data/data_",stade,"_",year,'.Rdata',sep=""))  -->

<!-- load(paste0(stade,"/results/Results_",stade,"_",year,".RData")) -->

<!-- adu <- as.matrix(fit$sims.matrix) -->

<!-- mcmc <- as.matrix(adu[,paste0("e_tot[",1:data$Y,"]")]) # 1984 to now) -->

<!-- s <- t(apply(mcmc,2,quantile,probs=c(0.025, .5, 0.975))) -->

<!-- #png(paste0(site,"/total_return.png"),width = 780, height = 480) -->

<!-- par(mfrow=c(1,1))  -->

<!-- ### Total number of returns -->

<!-- plot(NULL,xlim=c(0,1000),ylim=c(0,50000),bty="n",ylab="Recruitment (tacon 0+)",xlab="Stock (escapted adults)") -->

<!-- #axis(side=1,line=1,labels = years,at=1:data$Nyear, las=2, cex=.5) -->

<!-- # Stock -->

<!-- segments(s[,"2.5%"], r[2:27,"50%"],s[,"97.5%"],r[2:27,"50%"], col=paste0(mycol[1])) -->

<!-- segments(s[,"50%"], r[2:27,"2.5%"],s[,"50%"],r[2:27,"97.5%"], col=paste0(mycol[1])) -->

<!-- points(s[1:26,"50%"],r[2:27,"50%"],col=mycol[1],pch=21,bg=paste0(mycol[1])) -->

<!-- text(s[1:26,"50%"],r[2:27,"50%"]+2000,labels = years, cex=.5) -->

<!-- ``` -->
